An Invariant Framework for Conducting Reproducible Computational Science

### 2015-01-15 evaluation.tex
Split the time, add citiations

\begin{table}
    \centering
    \begin{tabular}{lccc}
    \hline
    \bf Tool Type & \bf Package Creation Time & \bf Re-Execution Time & \bf Package Size \\ \hline
	Parrot & 27 min 15 sec & 10 min 24 sec & 17.57 GB \\ \hline
	PTU & 23 min 30 sec & 8 min 40 sec & 17.57 GB \\ \hline 
    \end{tabular}
    \caption{Performance Comparison between Parrot and PTU}
    \label{table:parrot_ptu}
\end{table}

Table~\ref{table:parrot_ptu} compares the performance of preserving the Tauroast application using Parrot and PTU.
PTU accommplishes the execution procedure and packaging procedure concurrently through multi-threading, bringing 17.5\% additional time overhead.
Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist (takes 22 min 50 sec); second, traverse the namelist and copy all the accessed files into a self-contained package (takes 4 min 25 sec).

>>>>

\begin{table}
    \centering
    \begin{tabular}{lccc}
    \hline
    \bf Tool Type & \bf Obtain Namelist & \bf Create Package & \bf Re-Execution \\ \hline
	Parrot & 22 min 50 sec  & 4 min 25 sec & 10 min 24 sec \\ \hline
	PTU & --- & 23 min 30 sec & 8 min 40 sec \\ \hline 
    \end{tabular}
    \caption{Time Comparison between Parrot and PTU}
    \label{table:parrot_ptu}
\end{table}

Table~\ref{table:parrot_ptu} compares the time overhead of preserving the Tauroast application using Parrot and PTU.
Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist (takes 22 min 50 sec); second, traverse the namelist and copy all the accessed files into a self-contained package (takes 4 min 25 sec).
PTU accommplishes the execution procedure and the package creation procedure concurrently through multi-threading, bringing 17.5\% additional time overhead.

### 2015-01-15 measure.tex
Split the time, add citiations

Parrot~\cite{parrot-scpe} is a virtual filesystem access tool which
is used to attach applications to a variety of remote I/O systems such as HTTP, FTP, and CVMFS. It works by trapping system calls through the {\tt ptrace} interface,
replacing selected operations with remote accesses.  As a side-effect, Parrot is
also able to modify the filesystem namespace in arbitrary ways according to user
needs.  Parrot is particularly used in the high energy physics community
to provide remote access to application software.
To capture dependencies, we made small modifications to Parrot to record
the logical name of every file accessed by an application into an external
dependency list.  After execution is complete, a second tool is used to copy
all of the named dependencies into a package.

PTU~\cite{ptu} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.   PTU uses the the CDE~\cite{cde} technology to observe system calls, but takes a snapshot of every file at the point of access.  In addition to files, PTU records \emph{metadata} about the execution environment, such as kernel versions, application versions, and dynamic library versions by using standard Unix commands.  PTU also records \emph{provenance} in the form of a graph that describes how each file is created or consumed by processes within the application.  Because PTU is focused solely on the problem of preservation, it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.

>>>>

Parrot~\cite{thain2005parrot} is a virtual filesystem access tool which
is used to attach applications to a variety of remote I/O systems such as HTTP, FTP, and CVMFS. It works by trapping system calls through the {\tt ptrace} interface,
replacing selected operations with remote accesses.  As a side-effect, Parrot is
also able to modify the filesystem namespace in arbitrary ways according to user
needs.  Parrot is particularly used in the high energy physics community
to provide remote access to application software.
To capture dependencies, we made small modifications to Parrot to record
the logical name of every file accessed by an application into an external
dependency list.  After execution is complete, a second tool is used to copy
all of the named dependencies into a package.

PTU~\cite{pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.   PTU uses the the CDE~\cite{guo2011cde} technology to observe system calls, but takes a snapshot of every file at the point of access.  In addition to files, PTU records \emph{metadata} about the execution environment, such as kernel versions, application versions, and dynamic library versions by using standard Unix commands.  PTU also records \emph{provenance} in the form of a graph that describes how each file is created or consumed by processes within the application.  Because PTU is focused solely on the problem of preservation, it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.
